---
output: github_document
---

<!-- README.md is generated from README.Rmd. -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "65%"
)
```

# tvdenoising

<!-- badges: start -->
[![R-CMD-check](https://github.com/glmgen/tvdenoising/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/glmgen/tvdenoising/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/tvdenoising)](https://CRAN.R-project.org/package=tvdenoising)
<!-- badges: end -->

The `tvdenoising` package provides an implementation of an efficient linear-time
dynamic programming algorithm for univariate total variation denoising, due to
[Johnson (2013)](https://doi.org/10.1080/10618600.2012.681238), which computes
the exact solution, for a given regularization level $\lambda$. You can also 
find a concise explanation of the algorithm at 
[this link](https://www.stat.berkeley.edu/~ryantibs/papers/tvdp.pdf).

```{r tvd, echo=FALSE, dev="png", fig.width=5, fig.height=3, dpi=300}
library(tvdenoising)
set.seed(3)
n = 100
d = floor(n/5)
y = rep(c(8,0,10,3,4), times=c(rep(d, 4), n-4*d)) + rnorm(n)
lambda = c(0.5, 1, 5, 10)
yhat = matrix(NA, nrow = n, ncol = length(lambda))
for (i in 1:length(lambda)) yhat[,i] = tvdenoising(y, lambda[i])

par(mar = rep(0.01, 4))
plot(y, col = "gray60")
matplot(yhat, type = "l", lty = 1, add = TRUE)
legend("topright", lty = 1, col = 1:length(lambda),
       legend = as.expression(sapply(lambda, function(val) 
         bquote(lambda == .(val)))))
```

## Installation

To install the released version from CRAN:

``` r
install.packages("tvdenoising")
```

To install the development version from GitHub:

``` r
# install.packages("pak")
pak::pak("glmgen/tvdenoising")
```
